Individual Report

### 2020-03-31 doc/450/RealEstate_Xuechun_Lu.Rmd
moved to 450 folder

## 2. Measure of goodness of fit and prediction power

@@

assessment_aggregate <- read.csv(here("RealEstate/data","assessment_aggregate.csv"))

tax_final <- read.csv(here("RealEstate/data","tax_final.csv"))
#head(tax_final)

>>>>

## 2. Measure of Goodness of Fit and Prediction Power

@@

assessment_aggregate <- read.csv(here("data","assessment_aggregate.csv"))

tax_final <- read.csv(here("data","tax_final.csv"))
#head(tax_final)
